---
title: "Mosquito-borne infectious disease"
author: "John Doe"
date: "`r Sys.Date()`"
output: 
  bookdown::gitbook:
    output_file: "Mosquito-borne_infectious_disease.html"
documentclass: book
bibliography:
- book.bib
- packages.bib
description: "This is a minimal example of using the bookdown package to write a book."
link-citations: true
github-repo: "rstudio/bookdown-demo"
site: bookdown::bookdown_site
---


# Abstract

Infectious diseases are illnesses caused by harmful organisms like bacteria, viruses, fungi, or parasites that invade our bodies. These invaders can spread from person to person through various means, from direct contact to airborne transmission. Throughout history, infectious diseases have had a profound impact on human society.They have caused massive death tolls, shaping demographics and influencing societal structures. The Black Death, for instance, is estimated to have wiped out a third of Europe's population in the 14th century. Even today, infectious diseases like HIV/AIDS, malaria, and tuberculosis continue to claim millions of lives globally, particularly in developing countries.Our study aims to delve deeper into this complex relationship between infectious diseases and human society. We want to understand how these diseases have shaped our past, how they influence our present, and how we can better prepare for future outbreaks. By examining specific diseases or focusing on broader trends, or by finding the mosquitoes’ abundance, an early warning system can be created to gain valuable insights that can guide public health policies, medical advancements, and societal responses to these ever-present challenges.

## Usage

Each **bookdown** chapter is an .Rmd file, and each .Rmd file can contain one (and only one) chapter. A chapter *must* start with a first-level heading: `# A good chapter`, and can contain one (and only one) first-level heading.

Use second-level and higher headings within chapters like: `## A short section` or `### An even shorter section`.

The `index.Rmd` file is required, and is also your first book chapter. It will be the homepage when you render the book.

## Render book

You can render the HTML version of this example book without changing anything:

1.  Find the **Build** pane in the RStudio IDE, and

2.  Click on **Build Book**, then select your output format, or select "All formats" if you'd like to use multiple formats from the same book source files.

Or build the book from the R console:

```{r, eval=FALSE}
bookdown::render_book()
```

To render this example to PDF as a `bookdown::pdf_book`, you'll need to install XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

## Preview book

As you work, you may start a local server to live preview this HTML book. This preview will update as you edit the book when you save individual .Rmd files. You can start the server in a work session by using the RStudio add-in "Preview book", or from the R console:

```{r eval=FALSE}
bookdown::serve_book()
```

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
